---
title: "RWorksheet#6"
author: "Krystal Rose M. Rizardo"
date: "2022-11-30"
output: pdf_document
---

```{r, vector = TRUE}
library(dplyr)
library(ggplot2)
```
```{r 1}
data(mpg)
mpg_dataset <- glimpse(mpg)
mpg_dataset

# Answer: There are 11 columns, and 234 rows in mpg data set.

```

```{r 2}
# Answer: Dodge Manufacturer has 37 models

model_dataset <- mpg_dataset %>% group_by(manufacturer) %>% count()
model_dataset
colnames(model_dataset) <- c("Manufacturer","Counts")
model_dataset
```

```{r 2.1}
# Answer: The model caravan 2wd contains the most variation

variation_dataset<- mpg_dataset %>% group_by(model) %>% count()
variation_dataset
colnames(variation_dataset) <- c("Model","Counts")
variation_dataset
```

```{r 2A}
unique_models <- mpg_dataset %>% group_by(manufacturer, model) %>% distinct() %>% count()
unique_models
colnames(unique_models) <- c("Manufacturer", "Model","Counts")
unique_models
```

```{r 2B}
plot(unique_models)
ggplot(unique_models, aes(x = Model, y = Counts )) + geom_point(color='purple')

```

```{r 3}
ggplot(unique_models, aes(x = Model, y = Manufacturer )) + geom_point(color='blue')
```

```{r 3A}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
# Answer: The ggplot displays the black points in the plots.
```

```{r, 3B}
# Answer: Yes, it is useful because the result is easier to see and analyze.

```


```{r 4}
cars <- mpg_dataset %>% group_by(model) %>% count()
cars
colnames(cars) <- c("Model","Counts")
cars

```

```{r 4A}
bargss <- ggplot(cars, aes( Model, Counts )) +
  geom_bar(stat = "identity")

bargss +
  coord_flip()
           
```

```{r 4B}
head(cars, n = 20)
```

```{r 5}
ggplot(mpg, mapping = aes(x = displ , y = cyl)) + labs(title = "Relationship between No. 
     of Cylinders and Engine Displacement") + geom_point(aes(color = "engine displacement"))

```

```{r 5B}
# Answer: The relationship of cylinders and Engine Displacement are mostly  consistent or stable

```


```{r 6}

drv_frontw <- subset(mpg, drv == 'f')
drv_frontw <- nrow(drv_frontw)
drv_frontw

wheeldrive <- subset(mpg, drv == 'r')
nrow(wheeldrive)
wheeldrive

fourwd <- subset(mpg, drv == '4')
nrow(fourwd)
fourwd

suv_car <- subset(mpg, class == 'suv')
nrow(suv_car)
suv_car

comp <- subset(mpg, class == 'compact')
nrow(comp)
comp

m_size <- subset(mpg, class == 'midsize')
nrow(m_size)
m_size

two_seater <- subset(mpg, class == '2seater')
nrow(two_seater)
two_seater

mini_van <- subset(mpg, class == 'minivan')
nrow(mini_van)
mini_van

p <- subset(mpg, class == 'pickup')
nrow(p)
p

sub_comp <- subset(mpg, class == 'subcompact')
nrow(sub_comp)
sub_comp

```

```{r 6A}
ggplot(mpg, aes(drv, class)) +
  geom_tile (aes(fill = class)) 
```

```{r 6B}
# Answer: The result shows that if there is a relationship between a class and drv, a tile was created.
```


```{r 7}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = "green"))
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), colour = "green")

# In the first code, the "colour = green" code was inside the function aes(), so it failed 
# to give a color green dots and the dots became red dots. on the other hand, the second code was executed and 
# was in its proper place or outside the aes() function,and in result the plot was shown accordingly.
```


```{r 8}
#Answer: The result is about the fuel economy data from 1999 to 2008 for 38 popular models of cars
```
#8 A. Which variables from mpg data set are categorical?
#The categorical in mpg dataset include: manufacturer, model, trans (type of transmission), 
#drv (front-wheel drive, rear-wheel, 4wd), fi (fuel type), and class (type of car).

#8 B. Which are continuous variables?
#The continuous variables in mpg include: displ (engine displacement in litres), cyl 
#(number of cylinders), cty (city miles/gallon), and hwy (highway gallons/mile)

#8 C. Plot the relationship between displ (engine displacement) and hwy(highway miles
# per gallon). Mapped it with a continuous variable you have identified in 
#5-b. What is its result? Why it produced such output?
```{r 8C}
ggplot( data = mpg) +
  geom_point(mapping = aes(x = displ , y = hwy, col = displ)) 

```

  
```{r 8.1c}
# It produced such output because we plot the relationship between the displ and hwy and its geom_point color should be mapped in with a continuous variable.
```

```{r 9}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=displ)) +
  geom_smooth(se =FALSE)
```

```{r 10}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=displ)) +
  geom_smooth(se =FALSE,method = lm)
```
