---
title: "RWorksheet_Rizardo3b"
author: "Krystal Rose M. Rizardo"
date: "2022-11-22"
output: pdf_document
---

```{r vector1_A}
respondents <- c (1:20)
  respondents

  sex <- c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2,2,1,2)
  sex
  
  fathers_occupation <- c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1)
  fathers_occupation  

  persons_atHome <- c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6)
  persons_atHome
  
  sibling_atschool <- c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2)
  sibling_atschool
  
  types_of_houses <- c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)
  types_of_houses
  
  census_data <-data.frame(respondents,sex,fathers_occupation,persons_atHome,sibling_atschool,types_of_houses)
  census_data  
  
```
```{r vector1_B}
summary(census_data)
```

#r vector1_C
#is the mean number of siblings attending is 5?
  #Answer: No, because the mean number of siblings attending is 2.95.


```{r vector1_D}
first_rdata <- subset(census_data[1:2, 1:6, drop =FALSE])
first_rdata 
```

```{r vector1_E}
second_rdata <- census_data[c(3,5), c(2,4)]
second_rdata
```

```{r vector1_F}
typeshouses <- types_of_houses
typeshouses
```

```{r vector1_G}
male_data <- data.frame(sex, fathers_occupation)
subset(male_data, sex == 1 & fathers_occupation == 1)
```

```{r vector1_H}
female_data <- data.frame(sex, sibling_atschool) 
subset(female_data, sex == 2 & sibling_atschool >= 5)
```

```{r vector2_A}
df = data.frame(Ints=integer(),
                    Doubles=double(), Characters=character(),
                    Logicals=logical(),
                    Factors=factor(),
                    stringsAsFactors=FALSE)
    print("Structure of the empty dataframe:")
    print(str(df))
```

#a. Describe the results.
    
    #Answer: the result in the R program shows empty table or null
    
#b. Interpret the graph.
    
    #Answer: The graph displays the sentiment of tweets per day. You can see that negative comments are mostly relevant each day. 
    #           There were nearly 2,500 more negative tweets than positive or neutral tweets on July 14, 2020.
    #           The next day, with a one-day interval, the data rises to nearly 4,500 negative tweets, 
    #           leading both positive and neutral tweets. On the third and fourth days, the number of negative tweets remained 
    #           unchanged, but the number of positive and neutral tweets decreases as well.
    #           On the fifth day, with a one-day interval, all of the tweets decrease.
    #           Finally, on the sixth day, the sentiment of tweets rose again.
    
    





